Response to the defense feedback

### 2021-06-01 Chapter-6/Chapter-6.tex
Updates from Overleaf

\subsection*{Cache Model} We use a simple cache model in this work. Recent work such as CaSym~\cite{Brotzman19Casym,182946} uses an LRU cache. First, there is no fundamental difficulties for us to adopt a more realistic cache models. Second, the LRU model is still a substantial simplification of a real cache. However, their choice of a logical model of cache can bring expensive overheads.

\subsection*{Leakages} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages. 
\section{Precise Analysis on Single-trace Attacks}
While recent work found many side-channel vulnerabilities,
we note that many of them have not been patched by developers.
Side-channels are ubiquitous in software and it would be difficult to fix all of them.
We need a tool that estimates the sensitivity of each vulnerability
so software engineers can focus on
``severe'' leakages. For example, \tool{} reports that
the modular exponentiation using square and multiply algorithms can
leak more information than a key validation function.

Software developers can use \tool{} to find severe vulnerabilities
and reason about countermeasures.
\tool{} estimates the amount of leaked information for each side-channel leakage
in one execution trace. \tool{} is useful for software
engineers to test programs and fix vulnerabilities.
The design, which is more precise in reporting true leakages as compared with other static
methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, obviously misses
leakages on unexplored traces. The amount of leaked information also depends on the secret key.
However, as the tool is intended for debugging and testing,
we think it is a software engineer's responsibility to select the input key and trigger
the path in which they are interested. It is not a problem for crypto software
since virtually all keys follow similar computational paths.

>>>>

\subsection*{Cache Model} We use a simple cache model in this work. Recent work such as CaSym~\cite{Brotzman19Casym,182946} uses an LRU cache. First, there is no fundamental difficulties for us to adopt a more realistic cache models. Second, the LRU model is still a substantial simplification of a real cache. However, their choice of a logical model of cache can bring expensive overheads. As a result, CaSym can only analyze small code snippets.

\subsection*{Leakages} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has a few side-channel leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. \detect{} also detects several leakages in asymmetric ciphers such as RSA. After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which may partially explain why developers are not interested in fix all the side-channel leakages.

\section{Precise Analysis on Single-trace Attacks}
While recent work found many side-channel vulnerabilities,
we note that many of them are been patched by developers.
Side-channels are ubiquitous in software, and it is difficult to fix all of them.
We need a tool that estimates the sensitivity of each vulnerability
so software engineers can focus on
``severe'' leakages. For example, \tool{} reports that
the modular exponentiation using square and multiply algorithms can
leak more information than a key validation function.

Software developers can use \tool{} to find severe vulnerabilities
and reason about countermeasures.
\tool{} estimates the amount of leaked information for each side-channel leakage
in one execution trace. \tool{} is useful for software
engineers to test programs and fix vulnerabilities.
The design, which is more precise in reporting true leakages as compared with other static
methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, obviously misses leakages on unexplored traces. The amount of leaked information quantified by \tool{} also depends on the value of secret keys.
However, as the tool is intended for debugging and testing,
we think it is a software engineer's responsibility to select the input key and trigger
the path in which they are interested. It is not a problem for crypto software 
since virtually all keys follow similar computational paths.
